Effect of Black Hole Spins on Christodoulou Memory in Binary Mergers

### 2019-08-25 notes/Paper.tex
updated plots

	\includegraphics[width=3.0in]{../plots/MemoryGrowthtwoweeks.pdf}
	\includegraphics[width=3.0in]{../plots/ResedualGrowthtwoweeks.pdf}

@@

	\includegraphics[width=3.0in]{../plots/Memory_Spin_vs_Mass.pdf}
	\includegraphics[width=3.0in]{../plots/MemoryRes_Spin_vs_Mass.pdf}

@@

	\includegraphics[width=3.0in]{../plots/Memory_Spin_vs_Mass_tenyears.pdf}
	\includegraphics[width=3.0in]{../plots/MemoryRes_Spin_vs_Mass_tenyears.pdf}

>>>>

	\includegraphics[width=3.5in]{../plots/MemoryGrowthtwoweeks.pdf}
	\includegraphics[width=3.5in]{../plots/ResedualGrowthtwoweeks.pdf}

@@

	\includegraphics[width=3.5in]{../plots/Memory_Spin_vs_Mass.pdf}
	\includegraphics[width=3.5in]{../plots/MemoryRes_Spin_vs_Mass.pdf}

@@

	\includegraphics[width=3.5in]{../plots/Memory_Spin_vs_Mass_tenyears.pdf}
	\includegraphics[width=3.5in]{../plots/MemoryRes_Spin_vs_Mass_tenyears.pdf}
